NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-06-08 ms_nihao_budget.tex
correct one mistake about the normalization of Figure 2

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas ($10^7$K$ <
  T$), inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes {\bf are missing baryons. The missing
    mass been relocated past 2 virial radii, and is dominated by cool gas.}
   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with observational estimates.

%  Finally we show that the baryonic budget of most massive 
%  galaxies in NIHAO suite can match the observation for most 
%  components but the cool gas, which requires further 
%  theoretical and observational work to find the answer where
%  the cool gas actually is.
\end{abstract}

@@

{\bf The circum galactic medium (CGM) is a major potential  reservoir
  of the missing baryons. \hi{} and metal absorption lines are expected 
to exhibit such diffuse baryonic content. \hi{} is mainly from gas with
temperature T $\sim 10^4$ K so that it is able to detect cold gas in CGM.
Meanwhile, theoretical work has predicted that a substaince portion of 
CGM is in warm or hot phase with temperature T $> 10^{4.5}$ K, either
through photoionization, accretion shock or shock caused by galactic winds
\citep{voort12}. Such dilute halo gas is at T$\sim 10^{4.5-7}$ K, the detection
is dominated by metal line, e.g. \ovi{}.}  Recent advances in the detection of gas
in the CGM have come  from the COS survey \citep{Tumlinson11,
  Tumlinson13, Thom12,  Werk12, Werk13}.  On the scale of Milky Way
mass haloes $\Mhalo \sim 10^{12}\Msun$ a significant amount of warm
($10^4 < T < 10^7$K) gas has been detected \citep{Werk14}, accounting
for 33-88\% of the baryon budget. In the future such observations will
be extended to a wider range of halo masses.
{\bf A number of large volume cosmological simulations \citep{Ford13, Ford15,
Suresh15b, Oppenheimer16} and zoom-in cosmological simulations \citep{Stinson12,
Hummels13, Shull14} have given the prediction for the \hi{} and
\ovi{} absorption line. \citet{Gutcke16}
compared the column density profile of \ovi{} and \hi{} in CGM of galaxies
of the cosmological hydrodynamical simulation suite NIHAO \citep{Wang15}
with observations, studied the covering fraction of dense \hi{}, looked
at the shape of the CGM and its chemical composition. The conclusion
shows the simulations can reproduce the observation properties well.}

%{\bf ??? To understand
%  the physical properties of the CGM and the origins of components in
%  each phase has been shown to be able to test the impact of feedback
%  models \citep{Sharma12,Marasco13}???
  {\bf The physical properties of the CGM has been shown to be able to
    test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
    predicted galactic halo baryon fractions of galaxies with halo
    masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
    cosmological hydrodynamical simulations with a well-constrained
    model for galactic outflows.  They found that, without the outflow
    model, the baryon fraction inside the virial radius is roughly the
    cosmic baryonic fraction, but with the outflow model, the baryon
    fraction is increasingly suppressed in lower mass haloes.  By
    comparing results at $z=3$ and $z=0$, they showed that large
    haloes remove their baryons at early times while small haloes lose
    baryons more recently due to the wind material taking longer to
    return to low-mass galaxies than high-mass galaxies.
%  
  \citet{Sokolowska16} studied the halo gas of three Milky way-sized
  galaxies using cosmological zoom-in simulations. They found that
  most of missing baryons actually resides in warm-hot and hot gas
  which contribute to 80\% of the total gas reservoir.  The recovered
  baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
  is sensitive to the feedback model so that a reliable spatial
  mapping of the warm-hot medium will provide  a stringent test for
  feedback models.}

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project. NIHAO galaxies are consistent with the stellar mass vs halo
mass relations from halo abundance matching since redshift $z\sim 4$
\citep{Wang15}, the galaxy star formation rate vs stellar mass
relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore,
the simulations make plausible predictions for the mass fractions and
physical locations of the warm and hot gas components.  We find that
all the haloes contain less baryons than expected according to the
cosmic baryonic fraction, but the missing fraction is strongly mass
dependent.

@@

%We study the baryonic budget using the full set simulations of the NIHAO project.  
%The large range of the mass covered by our simulations enables
%us see the baryon fractions and mass profiles of different 
%galaxies, depending on the halo mass and stellar content.

%% FIGURE 1
\begin{figure}
\centerline{
%  \psfig{figure=barbudget_linear_v3.eps,width=0.5\textwidth}}
%\centerline{
%  \psfig{figure=barbudget_v3.eps,width=0.5\textwidth}
  \psfig{figure=barbudget_linearlog.eps,width=0.5\textwidth}
}
\caption{Fractional baryon content of our NIHAO simulations  as a
  function of halo mass. The green points show the ratio between the
  baryonic mass (stars + gas) inside the virial radius and the total
  baryonic mass associated with the dark matter halo. The blue points
  show the corresponding fraction for the stars. The solid green line
  and shaded region shows a double power-law fit, together with the
  1$\sigma$ scatter. For the stellar mass fraction we show several
  relations from halo abundance matching.    The linear (upper panel)
  and logarithmic (lower panel) scales emphasize the large amount of
  ``missing'' baryons and the low star formation efficiencies.}
\label{fig:budget}
\end{figure}

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=budgetpro.eps,width=0.99\textwidth}
}
\caption{Radial profile of the mass fraction of the gas in each phase
         to total baryon mass in each radial bin 
         at z=0 for all galaxies in NIHAO sample.
         Each solid line is from one galaxy and color coded with
         the halo mass. {\bf tickmarks overlap. fix. use $R_{200}$ for virial radius}}
\label{fig:corona}
\end{figure*}

@@

We define the fiducial baryonic mass as:
\begin{equation}
M_{\rm b} \equiv M_{\rm b}(R_{200})= \frac{f_{\rm b}}{1-f_{\rm b}}M_{\rm dm}(R_{200}) 
\label{equ:mb}
\end{equation}
where the $M_{\rm dm}$ is the total dark matter mass in the halo, and
the $f_{\rm b} = \Omegab/\Omegam \sim 0.15$ is the cosmic baryon
fraction (the ratio between baryon density and mass density including baryonic mass
plus dark matter), so that the  $M_{\rm b}$ is the baryonic mass inside the
virial radius if the baryons follow the dark matter closely.

Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
component inside the virial radius  to the fiducial baryonic mass for
the most massive galaxy in each zoom-in region. We present the
fractions of total stellar mass (blue points), and the total baryonic
mass including stellar mass plus gas mass (green points).  For the
stellar mass fraction we also show the relations from the halo
abundance  matching \citep{Moster13, Behroozi13, Kravtsov14}.  The
grey area is the one sigma scatter around the mean value  from
\citet{Kravtsov14}.

We tried to capture the behavior of the baryonic mass fraction as a 
function of the halo mass using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line,
{\bf which is 0.151 for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.0518 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.}

@@

Fig.~\ref{fig:budget} shows that all haloes in our study contain less
than the universal fraction of baryons. The upper panel uses a linear
y-axis scale, which highlights the large amount of baryons that are
missing, especially in low mass haloes. The logarithmic scale in the
lower panel highlights the power-law nature of the relations.

Since the haloes we study are above the mass where the cosmic UV
background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons,
consistent with expectations from energy driven gas outflows
\citep[e.g.,][]{Dutton12}.

@@

{\bf In Fig.~\ref{fig:corona}, we present the radial distribution of
  gas in different phases at $z=0$, normalized to the total baryon
  mass profile, such that for a given halo the four phases add up to
  unity.  All simulations share a common attribute.  The cold gas (T$<
  10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
  where most stars in galaxies form.  In contrast, the cool ($10^4$K
  $<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
  located at large distances with roughly constant fractions up to 2
  times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
  for all galaxies in the NIHAO sample, with the maximum hot gas
  fraction at any radius being  less than 5\%.}

@@

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations. 
 The lines are color coded by their halo mass, which shows a
  clear trend that the more massive haloes preserve more baryons at
  all radii.}
\label{fig:rps}
\end{figure}

%% FIGURE 4
\begin{figure}
\centerline{
  \psfig{figure=missing_vr.eps,width=0.5\textwidth}
}
\caption{Baryon radius as function of total virial mass.
         The points are color coded by the ratio 
         between baryon radius and the virial radius of each galaxy.}
\label{fig:missvr}
\end{figure}

%% FIGURE 5
\begin{figure*}
\centerline{
  \psfig{figure=budget_inout.eps,width=0.99\textwidth}
}
\caption{Mass fraction of gas in four phases (relative to the fiducial
  baryonic mass within virial radius). The blue and red points are for
  gas  inside and outside the virial radius, respectively. Cool gas is
  the dominant component of the CGM in NIHAO simulations.}
\label{fig:inout}
\end{figure*}

@@

Each solid curve represents a halo, and the curves are colored by
their halo mass (red for high masses to blue for low masses).  Broadly
speaking, the curves have a similar shape, with a normalization that
depends on halo mass. They have a cusp in  the central region where the
stars and cold gas dominate, then become flat in the outer region.
More massive haloes have higher baryon fractions at all radii.  At
small radii, the baryon to dark matter ratio is higher than the cosmic
value due to gas dissipation.  Even beyond the virial radius, there is
little change in the baryon fraction up to 2 virial radii.  We thus
conclude that the missing baryons are well outside of the virial
radius.

%The curves show a gradual transition based on mass that confirms 
%what we find in Fig.~\ref{fig:budget}. 
%In general terms, the lowest mass halos have a small peak but drop
%relatively steeply until $\sim$ 0.2R$_{200}$, then the curves rise slowly.
%As the masses increase, the central peaks rise and the curves in the 
%outer part are flater.
%Finally, the most massive galaxies have an almost constant curve 
%which are close but still less than 1.

@@

{\bf In Fig.~\ref{fig:inout}, we calculate the fractions of gas (in each phase)
inside the virial radius (blue points) and between 
the virial and baryon radii (red points).
%
The upper-left panel shows the  fractions of cold gas. The fractions
of cold gas between the virial radius and baryon radius of galaxies with
halo masses in the range between $10^{9} \Msun$ to  $10^{10} \Msun$
are greater than 80\%. As the halo mass increases, this fraction goes
down dramatically, in the mass range between $10^{10} \Msun$ and
$10^{11} \Msun$ the fractions are less than  20\% for most of galaxies
and the fractions for galaxies with halo mass above $10^{11} \Msun$ are
almost 0.  For the cold gas inside the virial radius, the fractions
increase gradually as halo mass increases and the maximum fraction is
about 20\% with at a halo mass of $10^{12} \Msun$.
%
The upper-right panel shows the fractions of cool gas.  The fractions
of cool gas in region outside of virial radius  increase from 0 at
halo masses are $10^9 \Msun$ to 80\% at halo  masses are around
$10^{10} \Msun$ to $10^{11} \Msun$, then  decrease in higher mass
range and reach 0 again at halo masses are $10^{12} \Msun$. The cool
gas inside virial radius shares  a similar trend but the maximum
fraction is about 40\% at  halo masses are $10^{11} \Msun$.
%
The fractions for warm-hot gas are shown in the lower-left panel.
The trends of the gas inside and outside gas are quite similar
which increase as the halo masses increase monotonically and whose 
maximum values are only 20\%.
%
The hot gas shown in the lower-right panel and is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo mass 
below $10^{11}$, the majority of baryons associated with the
dark matter halo are in the cold and cool phases, 
and are located well outside of virial radius. For the gas inside
virial radius, the majority is cool gas for the galaxies with
halo masses are $10^{11} \Msun$ and when halo masses are higher
than $10^{11} \Msun$ the fractions of cold gas, cool gas and 
warm-hot gas are comparable.}

%% FIGURE 6
\begin{figure}
\centerline{
  \psfig{figure=budget.eps,width=0.5\textwidth}
}
\caption{Baryonic budget 
  of NIHAO haloes of mass $3.5\times 10^{11} < M_{200}/\Msun <
  3.5 \times 10^{12}$ (blue points 
  with 1$\sigma$ error bars) compared with observations of 
  $M_{200} \sim 10^{12}\Msun$ haloes (shaded regions)
  }
\label{fig:comparison}
\end{figure}

@@

@@

\item The missing baryons in all haloes are beyond 2 virial radii.

@@

@@

@@

% Properties of gas in and around galaxy haloes
\bibitem[van de Voort \& Schaye (2012)]{voort12} van de Voort, F., Schaye, J.\ 2012, \mnras, 423, 2991

@@

>>>>

\begin{abstract}
  We use the NIHAO galaxy formation simulations to make predictions
  for the baryonic budget  in present day galaxies ranging from dwarf
  ($\Mhalo\sim10^{10} \Msun$) to Milky Way ($\Mhalo\sim10^{12} \Msun$)
  masses.  The sample is made of 88 independent high resolution
  cosmological zoom-in simulations.  NIHAO galaxies reproduce key
  properties of observed galaxies, such as the stellar mass vs halo
  mass and cold gas vs stellar mass relations. Thus they make
  plausible predictions for the baryon budget.  We present the mass
  fractions of stars, cold gas ($T<10^4$K), cool gas ($10^4 < T <
  10^5$K), warm-hot gas ($10^5 < T < 10^7$K), and hot gas ($10^7$K$ <
  T$), inside the virial radius, $R_{200}$.  Compared to the predicted
  baryon mass, using the dark halo mass and the universal baryon
  fraction, $f_{\rm b}\equiv \Omega_{\rm b}/\Omega_{\rm m}=0.15$, we
  find that all of our haloes {\bf are missing baryons. The missing
    mass been relocated past 2 virial radii, and is dominated by cool gas.}
   Haloes of mass $\Mhalo\sim 10^{10}\Msun$ are missing
  $\sim 90\%$ of their baryons.  More massive haloes ($\Mhalo\sim
  10^{12}\Msun$) retain a higher fraction of their baryons, with $\sim
  30\%$ missing, consistent with {\bf recent} observational estimates.
\end{abstract}

@@

{\bf The circum galactic medium (CGM) is a major potential  reservoir
  of the missing baryons. \hi{} and metal absorption lines are
  expected  to signpost such diffuse baryonic content. \hi{} is mainly
  from gas with temperature T $\sim 10^4$ K so that it is able to
  detect cold gas in the CGM.  Meanwhile, theoretical work has
  predicted that a substantial  portion of the CGM is in the warm or
  hot phase with temperature T $> 10^{4.5}$ K.  Gas enters this phase
  through photoionization, accretion shocks or shocks caused by
  galactic winds \citep{Voort12}. Such dilute halo gas is at T$\sim
  10^{4.5-7}$ K, so the detection is dominated by metal lines,
  e.g. \ovi{}.}  Recent advances in the detection of gas in the CGM
have come  from the COS survey \citep{Tumlinson11, Tumlinson13,
  Thom12,  Werk12, Werk13}.  On the scale of Milky Way mass haloes
$\Mhalo \sim 10^{12}\Msun$ a significant amount of warm ($10^4 < T <
10^7$K) gas has been detected \citep{Werk14}, accounting for 33-88\%
of the baryon budget. In the future such observations will be extended
to a wider range of halo masses.  {\bf A number of large volume
  cosmological simulations \citep{Ford13, Ford15, Suresh15b,
    Oppenheimer16} and zoom-in cosmological simulations
  \citep{Stinson12, Hummels13, Shull14} have given predictions for the
  \hi{} and \ovi{} absorption line. \citet{Gutcke16} compared the
  column density profile of \ovi{} and \hi{} in the CGM of galaxies
  from the NIHAO \citep{Wang15} cosmological hydrodynamical
  simulation suite with observations, studied the covering fraction of
  dense \hi{}, looked at the shape of the CGM and its chemical
  composition. The conclusion shows the simulations can reproduce the
  observation properties well.}

  {\bf The physical properties of the CGM has been shown to be able to
    test feedback models \citep{Sharma12,Marasco13}.  \citet{Dave09}
    predicted galactic halo baryon fractions of galaxies with halo
    masses ranging from $10^{11} \Msun$ to $10^{13} \Msun$ using
    cosmological hydrodynamical simulations with a well-constrained
    model for galactic outflows.  They found that, without the outflow
    model, the baryon fraction inside the virial radius is roughly the
    cosmic baryonic fraction, but with the outflow model, the baryon
    fraction is increasingly suppressed in lower mass haloes.  By
    comparing results at $z=3$ and $z=0$, they showed that large
    haloes remove their baryons at early times while small haloes lose
    baryons more recently due to the wind material taking longer to
    return to low-mass galaxies than high-mass galaxies.
%  
  \citet{Sokolowska16} studied the halo gas of three Milky way-sized
  galaxies using cosmological zoom-in simulations. They found that
  most of missing baryons actually resides in warm-hot and hot gas
  which contribute to 80\% of the total gas reservoir.  The recovered
  baryon fraction within 3 virial radii is 90\%.  The warm-hot medium
  is sensitive to the feedback model so that a reliable spatial
  mapping of the warm-hot medium will provide  a stringent test for
  feedback models.}

In this paper we make predictions for the baryonic budget for stars,
cold, warm and hot gas in and around the virial radius of haloes of
mass ranging from $\Mhalo\sim 10^{10}\Msun$ to $10^{12}\Msun$. We use
a sample of 88 zoom-in galaxy formation simulations from the NIHAO
project.
{\bf Reproducing the stellar mass content in dark matter haloes both
  today and in the past has been a formidable challenge for cosmological galaxy
  formation simulations \citep{Weinmann12, Hopkins14}. Even the latest
  state-of-the art simulations have trouble: the ILLUSTRIS simulation
  \citep{Vogelsberger14} strongly overpredicts the stellar masses in
  dwarf galaxy haloes $(M_{200} \lta 10^{11}\Msun)$, while the EAGLE
  simulations \citep{Schaye15} underpredict the peak of the star
  formation efficiency in halos of mass $M_{200}\sim 10^{12}\Msun$. In
  contrast, the} NIHAO galaxies are consistent with the stellar mass
vs halo mass relations from halo abundance matching since redshift
$z\sim 4$ \citep{Wang15}, the galaxy star formation rate vs stellar
mass relation since $z\sim 4$ \citep{Wang15}, and the cold gas mass vs
stellar mass relation at $z\sim 0$ \citep{Stinson15}.  Therefore, the
simulations make plausible predictions for the mass fractions and
physical locations of the warm and hot gas components.  We find that
all the haloes contain less baryons than expected according to the
cosmic baryonic fraction, but the missing fraction is strongly mass
dependent.

@@

%% FIGURE 1
\begin{figure}
\centerline{
%  \psfig{figure=barbudget_linear_v3.eps,width=0.5\textwidth}}
%\centerline{
%  \psfig{figure=barbudget_v3.eps,width=0.5\textwidth}
  \psfig{figure=barbudget_linearlog.eps,width=0.48\textwidth}
}
\caption{Fractional baryon content of our NIHAO simulations  as a
  function of halo mass. The green points show the ratio between the
  baryonic mass (stars + gas) inside the virial radius and the total
  baryonic mass associated with the dark matter halo. The blue points
  show the corresponding fraction for the stars. The solid green line
  and shaded region shows a double power-law fit, together with the
  1$\sigma$ scatter. For the stellar mass fraction we show several
  relations from halo abundance matching.    The linear (upper panel)
  and logarithmic (lower panel) scales emphasize the large amount of
  ``missing'' baryons, and the power-law nature of the relations,
  respectively.}
\label{fig:budget}
\end{figure}

@@

We define the fiducial baryonic mass as:
\begin{equation}
M_{\rm b} \equiv M_{\rm b}(R_{200})= \frac{f_{\rm b}}{1-f_{\rm b}}M_{\rm dm}(R_{200}) 
\label{equ:mb}
\end{equation}
where the $M_{\rm dm}$ is the total dark matter mass of the halo, and
the $f_{\rm b} = \Omegab/\Omegam \sim 0.15$ is the cosmic baryon
fraction (the ratio between baryon density and mass density including baryonic mass
plus dark matter), so that $M_{\rm b}$ would be the baryonic mass inside the
virial radius if the baryons followed the dark matter closely.

Fig.~\ref{fig:budget} shows the ratio between the  mass of each baryon
component inside the virial radius  to the fiducial baryonic mass for
the most massive galaxy in each zoom-in region. We present the
fractions of total stellar mass (blue points), and the total baryonic
mass including stellar mass plus gas mass (green points).  For the
stellar mass fraction we also show the relations from the halo
abundance  matching \citep{Moster13, Behroozi13, Kravtsov14}.  The
grey area is the one sigma scatter around the mean value  from
\citet{Kravtsov14}.
Fig.~\ref{fig:budget} shows that all haloes in our study contain less
than the universal fraction of baryons. The upper panel uses a linear
y-axis scale, which highlights the large amount of baryons that are
missing, especially in low mass haloes. The logarithmic scale in the
lower panel highlights the power-law nature of the relations.

@@

Since most of the haloes we study are above the mass where the cosmic UV
background prevents gas from cooling, the missing baryons have most
likely been ejected from the central galaxies in supernova/stellar
feedback driven winds.  Although the lower mass galaxies have
converted a smaller fraction of their available baryons into stars,
and hence there is proportionally less energy available to drive an
outflow, they have expelled a larger fraction of their baryons,
consistent with expectations from energy driven gas outflows
\citep[e.g.,][]{Dutton12}.

The behavior of the baryonic mass fraction, $f_{\rm bar}$, as a 
function of the halo mass is captured using a double power law formula:
\begin{equation}
\frac{f}{f_0} = \left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\alpha 
                        \left\{ 0.5 \left[ 1+\left( 
                        \frac{M_{200}}{\mathcal{M}_0} 
                        \right)^\gamma \right] 
                        \right\}^{\frac{\beta-\alpha}{\gamma}}.
\end{equation}
In this formula, the lower and higher mass ends have logarithmic slope
$\alpha$ and $\beta$, respectively, while $\gamma$ regulates how 
sharp the transition is from the lower to the higher ends.
The best fit parameters are as follows:
\begin{eqnarray}
\mathcal{M}_0  &=&  6.76 \times 10^{10} \nonumber \\
f_0  &=&   0.336 \nonumber \\
\alpha  &=&   0.684 \\
\beta  &=&   0.205 \nonumber \\
\gamma  &=&   3.40\nonumber  
\end{eqnarray}
The green shaded region indicates the scatter about the best fit line,
{\bf which is 0.151 for haloes with mass in the range of  
$3\times 10^{9}\Msun < M_{200} <2\times 10^{10} \Msun$, 0.236 for
halo mass in 
$2\times 10^{10}\Msun < M_{200} < 7\times 10^{10} \Msun$,
0.125 for halo mass in
$7\times 10^{10}\Msun < M_{200} < 3\times 10^{11} \Msun$
and 0.0518 for halo mass in
$3\times 10^{11}\Msun < M_{200} < 3.5\times 10^{12} \Msun$.

As might be expected, haloes with the highest masses we study have
high baryon fractions with relatively  small scatter. As halo mass
decreases, the baryon fraction decreases and the scatter increases,
consistent with expectations from outflows driven by stellar
feedback. At the lowest halo masses we study, below $10^{10}\Msun$,
the scatter starts to decrease. By contrast the scatter in the stellar
mass fraction increases below this scale. Thus it seems unlikely that
stellar feedback is primarily responsible for the low baryon
fractions.  Rather, we suggest an increased importance of the UV
background, which heats gas to above the virial temperature, thus
preventing it from collapsing into the low mass haloes.}

@@

%% FIGURE 2
\begin{figure}
\centerline{
  \psfig{figure=budgetpro.eps,width=0.48\textwidth}
}
\caption{Radial profile of the mass fraction of the gas in each phase
         to total baryonic mass in each radial bin 
         at $z=0$ for all galaxies in NIHAO sample.
         Each solid line is from one galaxy and colour coded with
         the halo mass.}
\label{fig:corona}
\end{figure}

{\bf In Fig.~\ref{fig:corona}, we present the radial distribution of
  gas in different phases at $z=0$, normalized to the total baryonic
  mass profile, such that, in the region far away from central galaxy
  where the stars are rare, for a given halo the four phases add up to
  unity.  All simulations share a common attribute.  The cold gas (T$<
  10^4$ K) is mostly located  near the center  ($R < 0.2 R_{200}$)
  where most stars in galaxies form.  In contrast, the cool ($10^4$K
  $<$ T $<$ $10^5$K) and  warm-hot ($10^5$K $<$ T $<$ $10^7$K) gas are
  located at large distances with roughly constant fractions up to 2
  times $R_{200}$.  The hot gas (T$>10^7$K) is a minority component
  for all galaxies in the NIHAO sample, with the maximum hot gas
  fraction at any radius being  less than 5\%.}

@@

@@

Each solid curve represents a halo, and the curves are coloured by
their halo mass (red for high masses to blue for low masses).  Broadly
speaking, the curves have a similar shape, with a normalization that
depends on halo mass. They have a cusp in  the central region where the
stars and cold gas dominate, then become flat in the outer region.
More massive haloes have higher baryon fractions at all radii.  At
small radii, the baryon to dark matter ratio is higher than the cosmic
value due to gas dissipation.  Even beyond the virial radius, there is
little change in the baryon fraction up to 2 virial radii.  We thus
conclude that the missing baryons are well outside of the virial
radius.

%% FIGURE 3
\begin{figure}
\centerline{
  \psfig{figure=ratioprofile.eps,width=0.5\textwidth}
}
\caption{Baryon distribution of each galaxy from NIHAO simulations. 
 The lines are colour coded by their halo mass, which shows a
  clear trend that the more massive haloes preserve more baryons at
  all radii.}
\label{fig:rps}
\end{figure}

@@

%% FIGURE 4
\begin{figure}
\centerline{
  \psfig{figure=missing_vr.eps,width=0.5\textwidth}
}
\caption{Baryon radius as function of total virial mass.
         The points are colour coded by the ratio 
         between baryon radius and the virial radius of each galaxy.}
\label{fig:missvr}
\end{figure}

%% FIGURE 5
\begin{figure*}
\centerline{
  \psfig{figure=budget_inout.eps,width=1.0\textwidth}
}
\caption{Mass fraction of gas in four phases (relative to the fiducial
  baryonic mass within the virial radius). The blue and red points are for
  gas  inside and outside the virial radius, respectively. Cool gas is
  the dominant component of the CGM in the NIHAO simulations.}
\label{fig:inout}
\end{figure*}

{\bf In Fig.~\ref{fig:inout}, we show the fractions of gas (in each
  phase) inside the virial radius (blue points) and between  the
  virial and baryon radii (red points).
  %
  The fractions of cold gas,
  $f_{\rm cold}$, are shown in the upper-left panel.  Inside the
  virial radius $f_{\rm cold}$ increases gradually from zero at a halo
  mass of $10^{10}\Msun$ to $\sim 20\%$ at a halo mass of
  $10^{12}\Msun$.  The gas outside the virial radius has the opposite
  and much stronger trend: $f_{\rm cold}\sim 50\%$ in haloes of mass
  $10^{10}\Msun$ and decreases to zero by halo masses of
  $10^{11}\Msun$.
  %
  The fractions of cool gas, $f_{\rm cool}$, are
  shown in the upper-right panel.  Inside the virial radius, $f_{\rm
    cool}$, has a maximum of 40\% at a halo mass of $10^{11} \Msun$,
  and declines to less than 10\% below and above halo masses of
  $10^{10}\Msun$ and $10^{12}\Msun$, respectively.  For most haloes there
  is more cool gas outside than inside the virial radius.  In haloes
  of mass $10^{10}\Msun$, $f_{\rm cool}\sim 80\%$, and decreases to
  less than 10\% by a halo mass of $10^{12}\Msun$.
%
The fractions for warm-hot gas,$f_{\rm warm}$,  are shown in the
lower-left panel.  The trends of the gas inside and outside the virial
radius are quite similar, $f_{\rm warm}$ increases monotonically with
halo mass with maximum values of $\sim 30\%$.
%
The hot gas shown in the lower-right panel and is negligible both
inside and outside the virial radius across the whole mass range we
study.
%
We thus conclude that, for galaxies with halo masses in the range
$10^{10} \lta M_{200}\lta 10^{11} \Msun$, the majority of baryons
associated with the dark matter halo are in the cold and cool phases,
and are located well outside of virial radius.  For haloes in the mass
range $10^{11} \lta M_{200}\lta 10^{12} \Msun$, the fractions of cold
gas, cool gas and  warm-hot gas are comparable.}

@@

%% FIGURE 6
\begin{figure}
\centerline{
  \psfig{figure=budget.eps,width=0.5\textwidth}
}
\caption{Baryonic budget 
  of NIHAO haloes of mass $3.5\times 10^{11} < M_{200}/\Msun <
  3.5 \times 10^{12}$ (blue points 
  with 1$\sigma$ error bars) compared with observations of 
  $M_{200} \sim 10^{12}\Msun$ haloes (shaded regions). There is good agreement, except for the cool gas which has two conflicting measurements.
  }
\label{fig:comparison}
\end{figure}

@@

\item The missing baryons from all haloes are located beyond 2 virial radii.

@@

% Galaxies on FIRE (Feedback In Realistic Environments): stellar
% feedback explains cosmologically inefficient star formation
\bibitem[Hopkins et al.(2014)]{Hopkins14} Hopkins, P.~F., Kere{\v s}, D., O{\~n}orbe, J., et al.\ 2014, \mnras, 445, 581

@@

% The EAGLE project: simulating the evolution and assembly of
% galaxies and their environments
\bibitem[Schaye et al.(2015)]{Schaye15} Schaye, J., Crain,
  R.~A., Bower, R.~G., et al.\ 2015, \mnras, 446, 521

@@

% Properties of gas in and around galaxy haloes
\bibitem[van de Voort \& Schaye (2012)]{Voort12} van de Voort, F., Schaye, J.\ 2012, \mnras, 423, 2991

%	Introducing the Illustris Project: simulating the coevolution
% of dark and visible matter in the Universe
\bibitem[Vogelsberger et al.(2014)]{Vogelsberger14} Vogelsberger, M., 
Genel, S., Springel, V., et al.\ 2014, \mnras, 444, 1518

@@

%  A fundamental problem in our understanding of low-mass galaxy evolution
  \bibitem[Weinmann et al.(2012)]{Weinmann12} Weinmann, S.~M., Pasquali, A., Oppenheimer, B.~D., et al.\ 2012, \mnras, 426, 2797
